Efficiently stable presentations from error-correcting codes

### 2023-10-27 efficient_stability.tex
Updates from Overleaf

\appendix
\section{Lower bounds on the modulus of stability of \eqref{eq:z2-efficient}}\label{appendix:lower_bounds}
In this Appendix we prove Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}, and deduce some corollaries from it. 
Before diving into the proof, we first sketch the idea behind it. 
We provide a method for translating every graph $([k],E\subseteq{\binom{[k]}{2}})$ into a collection of order $2$ unitaries $A_1,...,A_k$ (actually, permutations) that satisfy that
\begin{equation}\label{eq:commuting_or_not}
   \forall ij\in \binom{[k]}{2}\ \colon\ \ \|A_iA_j-A_jA_i\|_\tau^2=\begin{cases}
    2 & ij\in E,\\
    0 & ij\notin E.
\end{cases} 
\end{equation}
Therefore, these unitaries correspond to a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of \eqref{eq:z2-efficient}. For any pair $ij\in E$ we have $\|A_iA_j-A_jA_i\|_\tau^2=2$, and thus the unitaries $A_i$ and $A_j$ would need to be changed  by some constant amount to make them commute. Thus, to fix the $A_i$'s into a genuine representation of $\Z_2^k$, we would need to move them by at least a constant times the proportion of the largest   matching which embeds in $E$. Hence, by choosing a graph which is already a  matching with $c$ edges, we deduce the Lemma.

>>>>

\appendix
\section{Lower bounds on the modulus of stability of \eqref{eq:z2-efficient}}\label{appendix:lower_bounds}
In this Appendix we prove Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}, and deduce some corollaries from it. 
Before diving into the proof, we first sketch the idea behind it. 
We provide a method for translating every graph $([k],E\subseteq{\binom{[k]}{2}})$ into a collection of order $2$ unitaries $A_1,...,A_k$ (actually, permutations) that satisfy that
\begin{equation}\label{eq:commuting_or_not}
   \forall ij\in \binom{[k]}{2}\ \colon\ \ \|A_iA_j-A_jA_i\|_\tau^2=\begin{cases}
    2 & ij\in E,\\
    0 & ij\notin E.
\end{cases} 
\end{equation}
Therefore, these unitaries correspond to an $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of \eqref{eq:z2-efficient}. For any pair $ij\in E$ we have $\|A_iA_j-A_jA_i\|_\tau^2=2$, and thus the unitaries $A_i$ and $A_j$ would need to be changed  by some constant amount to make them commute. Thus, to fix the $A_i$'s into a genuine representation of $\Z_2^k$, we would need to move them by at least a constant times the proportion of the largest   matching which embeds in $E$. Hence, by choosing a graph which is already a  matching with $c$ edges, we deduce the Lemma.
